General burst analysis -- 4/18/2018

### 2018-10-29 resistingrhythm/analysis/burst_analysis.Rmd
Update misc analysis notebooks

exp_code <- 16
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(0, 1)

>>>>

# exp_code <- 16
# osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
# osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
# stim_codes <- c(0, 1)

# exp_code <- 32
# osc_codes <- c(500, 501, 502, 503, 504, 505, 510, 515, 520, 525, 530, 535, 540, 545, 550, 555, 560)
# osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
# stim_codes <- c(0, 1)

exp_code <- "103e"
osc_codes <- c(500, 501, 502, 503, 504, 505, 510, 515, 520, 525, 530)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
stim_codes <- c(3, 4)
